Region-network sparsity priors for\\ high-dimensional inference in fMRI data

### 2015-12-31 paper/paper.tex
blah

structured sparsity
extend trend in stastical modelling from
processing of auditory signals \cite{daudet2004sparse},
natural images \cite{harzallah2009combining} and
videos \cite{kang2015structured, kim2010sparse}
to
genetics \cite{rapaport2008classification, kim2012tree}
and
conformational dynamics of protein complexes \cite{jenatton2009structured}.

@@

@@

@@

@@

>>>>

structured sparsity
extend trend in stastical modelling from
processing of auditory signals \cite{daudet2004sparse},
natural images \cite{harzallah2009combining} and
videos \cite{kang2015structured, kim2010sparse}
to
genetics \cite{rapaport2008classification, kim2012tree},
astrophysics \cite{vinci2014estimating},
and
conformational dynamics of protein complexes \cite{jenatton2009structured}.

@@

 This L1/L2 norm for group lasso has been extended to a more general setting to

designed groups
 the child nodes enter the set of relevant inputs only if its parent node does.

@@

it is not realistic to assume that all of the tasks share the same set of rele- vant inputs as in the L1/L2-regularized regression. A subset of highly related outputs may share a common set of relevant inputs, whereas weakly related outputs are less likely to be affected by the same inputs.

@@

Among a collection of plau- sible models, the simplest one is often preferred

@@

However, in the problem of multi-task regression, where the output is a multivariate vector with an internal sparsity struc- ture, the estimation of the regression parameters can potentially benefit from taking into account this spar- sity structure in the estimation process. This will allow the strongly related output variables to be mapped to the input factors in a synergistic way, which is not possible in the standard lasso.
